Comparing MTurk and the US Population's Occupational Diversity

### 2018-10-04 Manuscript.Rmd
Fixed education analysis error on line 618 (now line 616). Also took out a few lines where it was viewing the tables in order for code to run smoother.

#Build Ethnicity table 
ethnicity_table <- cbind(MTurk_eth, ethCI, BLS_eth)
names(ethnicity_table) <- c("ethnicity", "n", "o", "LL_eth", "UL_eth", "e")
eth_table <- ethnicity_table[1:4 , c(1, 6, 2, 4, 3, 5)]
View(eth_table)

#Ethnicity chi squared test
eth_ch2 <- as.data.frame(chi2(eth_table))
names(eth_ch2) <- c("chi2")
row.names(eth_ch2) <- c("African American", "Asian", "Caucasian", "Hispanic")
eth_ch2 <- na.omit(eth_ch2)
View(eth_ch2)

@@

#Use vapply and the above function to get expected proportions from BLS data
BLS_edu <- sapply(BLS_education, prop_func)

@@

#Build Education table 
education_table <- cbind(MTurk_edu, eduCI, BLS_edu)
names(education_table) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
education_table <- education_table[ , c(1, 6, 2, 4, 3, 5)]
View(education_table)

#Education chi squared test
edu_ch2 <- as.data.frame(chi2(education_table))
names(edu_ch2) <- c("chi2")
row.names(edu_ch2) <- c("high school/GED" , "2 year degree", "4 year degree", "advanced degree")
edu_ch2 <- na.omit(edu_ch2)
View(edu_ch2)

>>>>

#Build Ethnicity table 
ethnicity_table <- cbind(MTurk_eth, ethCI, BLS_eth)
names(ethnicity_table) <- c("ethnicity", "n", "o", "LL_eth", "UL_eth", "e")
eth_table <- ethnicity_table[1:4 , c(1, 6, 2, 4, 3, 5)]

#Ethnicity chi squared test
eth_ch2 <- as.data.frame(chi2(eth_table))
names(eth_ch2) <- c("chi2")
row.names(eth_ch2) <- c("African American", "Asian", "Caucasian", "Hispanic")
eth_ch2 <- na.omit(eth_ch2)

@@

#Use vapply and the above function to get expected proportions from BLS data
BLS_edu <- sapply(BLS_education, e_prop)

@@

#Build Education table 
education_table <- cbind(MTurk_edu, eduCI, BLS_edu)
names(education_table) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
education_table <- education_table[ , c(1, 6, 2, 4, 3, 5)]

#Education chi squared test
edu_ch2 <- as.data.frame(chi2(education_table))
names(edu_ch2) <- c("chi2")
row.names(edu_ch2) <- c("high school/GED" , "2 year degree", "4 year degree", "advanced degree")
edu_ch2 <- na.omit(edu_ch2)
